Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-06-25 paper/paper.tex
new structure

\begin{abstract}
  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
  pristine conditions of the first galaxies in the Universe and
  are the best systems to test models on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad, single peaked, highly symmetric \lya\ line emission that had
evaded theoretical interpretation so far.  
In this paper we explain these features by two different physically
motivated kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
We find that both models independently require high velocities, either
a clump velocity dispersion of \sigmaclump\ with outflows of
\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$. 
The velocity dispersion in the multiphase model is consistent with a dynamical
mass of $2\times 10^{9}$ M$_{\odot}$, ten times its baryonic mass,
which can be explained if \tol\ is hosted by a dark matter halo of at least
$10^{11}$ M$_{\odot}$; conditions similar to those of Dwarf Elliptical Galaxies.
This work shows the importance of considering multiphase
and rotation kinematics among the possible conditions shaping the
\lya\ spectra.
If future kinematic maps of \tol\ confirm the velocities found by the
multiphase model, it will be the basis to study evolutionary processes that
might be at play during primordial galaxy evolution.
\end{abstract}

@@

We acknowledge that a final confirmation of our kinematic findings has
to be provided by new observational tests with integral field unit
spectroscopy. 
If our results are confirmed, this would open up a new line of more detailed
enquiries to understand how a compact dwarf galaxy can have the
structural characteristics similar to a dwarf elliptical while being
at the same time isolated and sustaining large starburst.
Such and investigation could provide an evolutionary between star forming
and quiescent stages of dwarf galaxy evolution.

>>>>

\begin{abstract}
  The conditions in star-forming Compact Dwarf Galaxies (CDGs) 
  place them as the best systems to test models on primordial
galaxy formation and evolution.    
Here we report on one of such CDGs, \tol, which presents
a broad, single peaked, highly symmetric \lya\ line emission that had
evaded theoretical interpretation so far.  
In this paper we explain these features by two different physically
motivated kinematic models: 
an interstellar medium composed by outflowing clumps with 
random motions and an homogeneous gaseous sphere undergoing solid body
rotation.
It is the first time that an observed \lya\ spectrum can be explained
assuming either of these kinematic conditions.
The multiphase model requires a clump velocity dispersion of
\sigmaclump\ with outflows of \inftyclump\ while the bulk rotation
velocity is constrained to be $348^{+75}_{-48}$ \kms.
This shows the importance of considering multiphase
and rotation kinematics among the possible conditions shaping the
\lya\ spectra.
However, we consider that the multiphase model has more chances to
agree with \tol's reality. 
The clump velocity dispersion implies a dynamical mass of $2\times
10^{9}$ M$_{\odot}$, ten times its baryonic mass, which can be
explained if \tol\ is hosted by a dark matter halo of at least
$10^{11}$ M$_{\odot}$; conditions similar to those of Dwarf Elliptical
Galaxies. 
If future kinematic maps of \tol\ confirm the velocities found by the
multiphase model, it could provide a new perspective to study
evolutionary processes linking star-forming with quiescent phases in
primordial galaxy evolution. 
\end{abstract}

@@

We acknowledge that a final confirmation of our kinematic findings has
to be provided by new observational tests with integral field unit
spectroscopy. 
If our results are confirmed, this would open up a new line of more detailed
enquiries to understand how a compact dwarf galaxy can have the
structural characteristics similar to a dwarf elliptical while being
at the same time isolated and sustaining large starburst.
Such and investigation could provide an evolutionary link between star-forming
and quiescent stages of dwarf galaxy evolution.
